---
title: "Bar Graphs"
output:
  html_document:
    df_print: paged
    theme: united # https://bootswatch.com/3/
    highlight: tango # default, tango, pygments, kate, monochrome, espresso, zenburn, haddock, and textmate
---

```{r include=FALSE}
library(gcookbook)
library(tidyverse)
library(ggthemes)
```

### `upc` Data

I’ll use the `uspopchange` data set for this example. It contains the percentage change in population for the US states from 2000 to 2010. I’ll take the top 10 fastest-growing states and graph their percentage change. 
```{r}
upc <- uspopchange %>%
  arrange(desc(Change)) %>%
  slice(1:10) %>% 
  select(State, Abb, Region, Change)
upc
```
\
\


### Grouping Bars Together

If I want to group bars together, I need to map a variable to `fill`, and use `geom_col(position="dodge")`.

```{r}
ggplot(upc, aes(x = Abb, y = Change, fill = Region)) +
  geom_col(position = "dodge") + theme_wsj()
```
\
\


### Sorting the bars

This example uses the `reorder()` function to reorder the levels of the factor `Abb` based on the values of `Change`

```{r}
ggplot(upc, aes(x = reorder(Abb, -Change), y = Change, fill = Region)) +
  geom_col(colour = "black") +
  scale_fill_manual(values = c("#669933", "#FFCC66")) 
```

### `climate_sub` Data
I'll use a subset of `climate` data and create a new column called `pos`, which indicates whether the value is positive or negative.

```{r}
climate_sub <- climate %>%
  filter(Source == "Berkeley" & Year >= 1900) %>%
  mutate(pos = Anomaly10y >= 0) %>% 
  select(Year, Anomaly10y, pos)

climate_sub
```



```{r}
ggplot(climate_sub, aes(x = Year, y = Anomaly10y, fill = pos)) +
  geom_col(position = "identity") +
  theme_wsj()
```


```{r}
ggplot(climate_sub, aes(x = Year, y = Anomaly10y, fill = pos)) +
  geom_col(position = "identity", colour = "black", size = 0.25) +
  scale_fill_manual(values = c("#CCEEFF", "#FFDDDD"), guide = FALSE)+
  theme_wsj()
```


```{r}
ggplot(cabbage_exp, aes(x = Date, y = Weight, fill = Cultivar)) +
  geom_col() + theme_wsj()
```
```{r}
ggplot(cabbage_exp, aes(x = Date, y = Weight, fill = Cultivar)) +
  geom_col(position = position_dodge2()) + theme_wsj()
```
```{r}
ggplot(cabbage_exp, aes(x = Date, y = Weight, fill = Cultivar)) +
  geom_col(position = "fill") + 
  scale_y_continuous(labels = scales::percent) +
  theme_wsj()
```


```{r}
ggplot(cabbage_exp, aes(x = Date, y = Weight, fill = Cultivar)) +
  geom_col(colour = "black", position = "fill") +
  scale_y_continuous(labels = scales::percent) +
  scale_fill_brewer(palette = "Pastel2") + theme_wsj()
```

```{r}

```







