---
title: "R Selenium"
output:
  html_document:
    df_print: paged
    theme: united # https://bootswatch.com/3/
    highlight: tango # default, tango, pygments, kate, monochrome, espresso, zenburn, haddock, and textmate
---
  
### Running Selenium Server
If I intend to drive a browser on the machine that RSelenium is running on, I need to have a ***Selenium Server*** running on the machine. The Selenium Server is needed in order to run Remote Selenium WebDriver.  

- Selenium RC [^1]

[^1]: Remote Control

- Download Selenium Standalone Server file. Click  [here](https://www.seleniumhq.org/download/).

- Open a console in my mashine and navigate to where the selenium Standalone Server jar file is located and run this code : `java -jar selenium-server-standalone-x.xx.x.jar`
\

### Connecting to a Running Server
`RSelenium` has a main reference class named `remoteDriver`. To connect to a server, I need to instantiate a new `remoteDriver` with appropriate options.
```{r eval=FALSE}
library(RSelenium)
remDr <- remoteDriver(
  remoteServerAddr = "localhost",
  port = 4444L,
  browserName = "chrome"
)
```
To connect to the server, user the `open` method:
```{r eval=FALSE}
remDr$open()
```



